Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-31 fmics/paper.tex
revise footnote about HOL

\subsection{Formal Model of SRS}
The first step to prove the correctness statement is to build a logical model of the SRS structure.
We model each building block of the SRS structure that holds a count value -- for example, each cell in each shift register -- as a function in HOL\footnote{Here, use of acronym HOL refers to the formal notation that can be parsed by HOL4. In this paper, we use a slightly variant of this notation to improve readability.} that takes the input stream and current time step as inputs and returns the value the corresponding building block holds at that time.

>>>>

\subsection{Formal Model of SRS}
The first step to prove the correctness statement is to build a logical model of the SRS structure.
We model each building block of the SRS structure that holds a count value -- for example, each cell in each shift register -- as a function in HOL\footnote{The acronym HOL refers to higher-order logic rather than the software tool HOL4.
We use the tool to define a function in the logic.}
